---
title: "<center> REACH Iraq MCNA 2020 - July-August, 2020 </center>"
output:
  html_document: default
  pdf_document: default
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>


```{r, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = FALSE,comment = NA, message = FALSE, warning=FALSE, fig.align = 'center' )
```

<!-- *** -->

```{r, include=FALSE}

library(lubridate)
library(kableExtra)
library(knitr)
library(readr)
library(readxl)
library(openxlsx)
library(sf)
library(raster)
library(leaflet)
library(htmltools)
library(tidyr)
library(dplyr)
library(plotly)


source("functions/audit_function_full.R")

WGS84 <- crs("+init=epsg:4326")
UTM38N <- crs("+init=epsg:32638")

assessment_start_date <- as.Date("2020-07-15")

# set min time and max # interviews per day
time_limit <- 12
flag_time_limit <- 25
max_interv <- 10

###########################################################################################################

# read data from excel file
df <- read_excel("input/raw_data/MCNA_VIII_2020_-_latest_version_-_False_-_2020-09-22-11-54-27.xlsx", sheet = "MCNA_VIII_2020") %>% 
  mutate(calc_noteligible = as.numeric(calc_noteligible),
         governorate_mcna = case_when(is.na(governorate_mcna) ~ governorate_mcna_r,
                                      TRUE ~ governorate_mcna),
         consent = case_when(is.na(consent) ~ consent_remote,
                             TRUE ~ consent))

###########################################################################################################
# time check from audit files
# today
df$today <- as.Date(df$start, "%Y-%m-%d")

df <- time_check_audit(df_raw = df, x_uuid = "_uuid", today = "today", time_limit = time_limit)
# df <- time_check(df, time_limit)

df <- df %>% 
  mutate(time_validity = case_when(interview_duration < flag_time_limit & 
                                     interview_duration > time_limit ~ "Flagged", TRUE ~ time_validity))

###########################################################################################################
# when survey does not continue to hh member calculation, these surveys are not valid
df <- df %>% 
  mutate(calc_noteligible = case_when(is.na(num_hh_member) ~ 1,
                                      TRUE ~ calc_noteligible))

# add population group
df <- df %>% 
  mutate(population_group = case_when(calc_noteligible == 1 ~ "not_eligible",
                                      calc_idp == 1 ~ "idp_out_camp",
                                      calc_returnee == 1 ~ "returnee",
                                      TRUE ~ "not_eligible"))

# remove ineligible surveys
df %<>% filter(consent == "yes" & population_group != "not_eligible")

########## SAMPLE FRAMES ########################
# In person sample
in_person_sample_df <- read_excel("input/sample/inperson_sf_14072020.xlsx")

in_person_sample_summarized <- in_person_sample_df %>% 
  group_by(pop_group_dist) %>% 
  summarise(num_surveys = sum(num_surveys))


# phone interview sample
phone_int_sample_df <- read_excel("input/sample/phone_int_sf_21072020.xlsx")


###########################################################################################################
# SPATIAL district check  for in person data collection #
############# Data frames for tracking ##############

in_person_points <- df %>% 
  filter(dc_method == "in_person") %>% 
  filter(!is.na(`_gpslocation_latitude`),!is.na(`_gpslocation_longitude`)) %>% 
  dplyr::select(`_uuid`,governorate_mcna,cluster_location_id,enumerator_num,population_group,lat=`_gpslocation_latitude`,long=`_gpslocation_longitude`) %>%  
  as_tibble()

points_sf <- in_person_points %>%
  dplyr::select(`_uuid`,governorate_mcna,cluster_location_id,enumerator_num,population_group,lat,long) %>%
  st_as_sf(
    coords = c("long", "lat"),
    agr = "constant",
    crs = WGS84,       
    stringsAsFactors = FALSE,
    remove = TRUE
  ) 

######### IRQ Dist boundary ###################

irq_dist <- st_read("input/spatial_data/irq_dist.geojson") %>% 
  mutate(district_gps = irq_dist_lookup_dist_kobo,
         District = irq_dist_lookup_dist_kobo)

irq_dist <- sf::st_as_sf(irq_dist, coords = c("long", "lat"), crs = 4326)
irq_dist <- sf::st_cast(irq_dist,"POLYGON") 

# spatial join points to get true districts of GPS locations
district_join <- st_join(points_sf, irq_dist) %>% 
  dplyr::select(`_uuid`:geometry, population_group, district_gps) 

# filter for IDP surveys
district_join_idp <- district_join %>% 
  filter(population_group == "idp_out_camp")

# filter for returnee surveys
district_join_returnee <- district_join %>% 
  filter(population_group == "returnee")

##
# convert back to df
district_join_df <- as.data.frame(district_join) %>% 
  dplyr::select(`_uuid`, district_gps) %>% 
  mutate(uuid = `_uuid`,
         district_gps = as.character(district_gps))

# merge back with main df to add actual district
df <- merge(df, district_join_df, all=T) 


# set district_mcna column to true district for in person surveys
df <- df %>% 
  mutate(district_mcna = case_when(!is.na(district_gps) ~ district_gps,
                                   TRUE ~ district_mcna))

# add full strata
df <- df %>% 
  mutate(strata = paste0(district_mcna, "_", population_group))


######## cluster points ######################

cluster_points <- st_read("input/spatial_data/inperson_sf.geojson",
                          fid_column_name = character(1)) %>%
  mutate(cluster_location_id = as.character(Place.id),
         id = Place.id)

row.names(cluster_points) <- cluster_points$Place.id


cluster_points <- st_as_sf(cluster_points, coords = c("long", "lat"), crs = 4326)

cluster_points_buff_2km <- st_buffer( cluster_points, 0.008)

# district_join$cluster_within <- st_is_within_distance(district_join, cluster_points, 0.08)

district_join <- st_join(district_join, cluster_points_buff_2km, left=T) 


district_join %<>%  mutate(in_cluster = case_when(is.na(id) ~ "no", TRUE ~ "yes")) %>% 
  dplyr::select(`_uuid`:district_gps, in_cluster)


#### deleted interviews

# Deleted interviews 
df <- df %>% 
  mutate(
    deleted = case_when(
      time_validity == "Deleted" | consent == "no" | population_group == "not_eligible" ~ "yes",
      TRUE ~ "no"
    )
  )

########################################################################################
### Interview method 

interview_method <- df %>% 
  dplyr::select(Date = today,
         Enumerator = enumerator_num,
         District = district_mcna,
         interview_type = dc_method
  ) %>% 
  group_by(District, interview_type) %>% tally(name = "Number_of_interviews")

interview_method_date <- df %>% 
  dplyr::filter(today > assessment_start_date) %>% 
  dplyr::select(Date = today,
         Enumerator = enumerator_num,
         District = district_mcna,
         interview_type = dc_method
  ) %>% 
  group_by(interview_type, Date) %>% tally(name = "Number_of_interviews")

survey_method_graph <- plot_ly(interview_method_date, x = ~Date, y = ~Number_of_interviews, name = 'High 2014', type = 'scatter', mode = 'lines',
        line = list(color = 'rgb(205, 12, 24)', width = 4)) 


# interview_method Wide format
interview_method_wide <- tidyr::pivot_wider(interview_method, 
                                            names_from = interview_type, 
                                            values_from = Number_of_interviews,
                                            values_fill = list(Number_of_interviews = 0)) %>% 
  dplyr::select(District, `Face to Face` = in_person, Phone = remote )

## Tracking by district - phone interviews #################################################### 

district_sample_phone <- phone_int_sample_df %>%
  dplyr::select(Governorate, District , pop_group, strata, Sample = num_int, Max_Sample = num_int_max) %>%
  arrange(Governorate)

district_tracking_phone <- df %>%
  dplyr::filter(dc_method == "remote") %>% 
  group_by(strata) %>%
  summarise(Submissions = n(),
            Short_intv = sum(time_validity == "Deleted", na.rm = T),
            Deleted = sum(deleted == "yes", na.rm = T),
            Accepted = sum(deleted == "no", na.rm = T)
  )

district_tracking_merged_phone <- left_join(district_sample_phone, district_tracking_phone, by = "strata")  %>%
  mutate(
    Remaining =  case_when(
      is.na(Accepted) ~ Sample,
      TRUE ~ (Accepted - Sample) * -1
    ),
    Remaining_Max =  case_when(
      is.na(Accepted) ~ Max_Sample,
      TRUE ~ (Accepted - Max_Sample) * -1
    )
  )

func <- function(z) if (is.numeric(z)) sum(z, na.rm = T) else ''
sumrow2 <- as.data.frame(lapply(district_tracking_merged_phone, func))
sumrow2$Governorate <- ""
sumrow2$District <- "Total"
district_tracking_merged_phone <- rbind(district_tracking_merged_phone, sumrow2 ) %>%
  mutate_all(
    funs(replace_na(.,0)))
##########################################################################################################
# join phone interview tracking to district sf object  #################################################### 
# IDP
iraq_dist_idp <- left_join(irq_dist, district_tracking_merged_phone, by = "District") %>% 
    mutate(pop_group_dist = strata) %>% 
  filter(pop_group == "idp_out_camp")%>% 
  mutate(perc_complete = round((Accepted/Max_Sample)*100),0)

# spatial intersect to get in person count by district
iraq_dist_idp$in_person_count <- lengths(st_intersects(iraq_dist_idp, district_join_idp))

# join with in person sample frame to get total surveys
iraq_dist_idp <- left_join(iraq_dist_idp, in_person_sample_summarized, by = "pop_group_dist")

iraq_dist_idp %<>%  mutate(perc_in_person_complete = round((in_person_count/num_surveys)*100),0,
                                remaining_in_person = num_surveys-in_person_count)

iraq_dist_idp %<>% mutate(final_perc_complete = case_when(in_person_count > 2 ~
                                                           perc_in_person_complete,
                                                           TRUE ~ perc_complete),
                          final_accepted = case_when(in_person_count > 2 ~ as.numeric(in_person_count),
                                                     TRUE ~ Accepted),
                          final_remaining = case_when(in_person_count > 2 ~ remaining_in_person,
                                                     TRUE ~ Remaining_Max))

iraq_dist_idp %<>% mutate(final_perc_complete = case_when(final_perc_complete > 99 ~ 100,
                          TRUE ~ final_perc_complete))


# returnee
iraq_dist_returnee <- left_join(irq_dist, district_tracking_merged_phone, by = "District") %>% 
    mutate(pop_group_dist = strata) %>% 
  filter(pop_group == "returnee") %>% 
  mutate(perc_complete = round((Accepted/Max_Sample)*100),0)

# spatial intersect to get in person count by district
iraq_dist_returnee$in_person_count <- lengths(st_intersects(iraq_dist_returnee, district_join_returnee))

# join with in person sample frame to get total surveys
iraq_dist_returnee <- left_join(iraq_dist_returnee, in_person_sample_summarized, by = "pop_group_dist")

iraq_dist_returnee %<>%  mutate(perc_in_person_complete = round((in_person_count/num_surveys)*100),0,
                                remaining_in_person = num_surveys-in_person_count)

iraq_dist_returnee %<>% mutate(final_perc_complete = case_when(in_person_count > 0 ~
                                                           perc_in_person_complete,
                                                           TRUE ~ perc_complete),
                          final_accepted = case_when(in_person_count > 0 ~ as.numeric(in_person_count),
                                                     TRUE ~ as.numeric(Accepted)),
                          final_remaining = case_when(in_person_count > 0 ~ remaining_in_person,
                                                     TRUE ~ Remaining_Max))

iraq_dist_returnee %<>% mutate(final_perc_complete = case_when(final_perc_complete > 99 ~ 100,
                          TRUE ~ final_perc_complete))

## Tracking by district - in person #################################################### 

district_sample_in_person <- in_person_sample_summarized  %>%
  dplyr::select(strata= pop_group_dist, Sample = num_surveys) 

district_tracking_in_person <- df %>%
  dplyr::filter(dc_method == "in_person") %>% 
  group_by(strata) %>%
  summarise(Submissions = n(),
            Short_intv = sum(time_validity == "Deleted", na.rm = T),
            Deleted = sum(deleted == "yes", na.rm = T),
            Accepted = sum(deleted == "no", na.rm = T)
  )

district_tracking_merged_in_person <- left_join(district_sample_in_person, district_tracking_in_person, by = "strata")  %>%
  mutate(
    Remaining =  case_when(
      is.na(Accepted) ~ Sample,
      TRUE ~ (Accepted - Sample) * -1
    )
  ) 

func <- function(z) if (is.numeric(z)) sum(z, na.rm = T) else ''
sumrow_in_person <- as.data.frame(lapply(district_tracking_merged_in_person, func))

district_tracking_merged_in_person <- rbind(district_tracking_merged_in_person, sumrow_in_person ) %>%
  mutate_all(
    funs(replace_na(.,0)))
########################################################################################

########################################################################################
# Started before date of data collection
started_before <- df %>% 
  filter(today < assessment_start_date) %>% 
  dplyr::select(Date = today,
         Enumerator = enumerator_num,
         District = district_mcna)


# Enumerator productivity

enumerator_productivity <- df %>% 
  filter(df$consent == "yes" & population_group != "not_eligible") %>% 
  group_by(Date = today, Enumerator = enumerator_num) %>% 
  summarise(Interviews = n())
enumerator_productivity_many <- enumerator_productivity %>% 
  dplyr::filter(Interviews > max_interv)

enumerator_productivity_less <- enumerator_productivity %>% 
  dplyr::filter(Interviews < 3)

enumerator_productivity_final <- rbind(enumerator_productivity_many, enumerator_productivity_less)%>% 
  arrange(desc(Date) )


# Enumerator per survey status 

enumer_per_survey_status <- df %>% 
  filter(df$consent == "yes" & population_group != "not_eligible") %>% 
  group_by(Date = today, Enumerator = enumerator_num) %>% 
  summarise(Accepted = sum(time_validity != "Deleted", na.rm = T),
            Deleted = sum(time_validity == "Deleted", na.rm = T )
  )

# Survey status per day 

survey_status_per_day <- df %>% 
    filter(df$consent == "yes" & population_group != "not_eligible") %>% 
  group_by(Date = today) %>% 
  summarise(Accepted = sum(time_validity != "Deleted", na.rm = T),
            Deleted = sum(time_validity == "Deleted", na.rm = T )
  )


# survey length by enumerator

survey_lenght <- df %>% 
    filter(df$consent == "yes" & population_group != "not_eligible") %>% 
  group_by(Enumerator = enumerator_num) %>% 
  summarise(
    Median_duration = round(median(interview_duration, na.rm = T),0)
  ) %>% 
  arrange(desc(Median_duration) )
  

overall_survey_median <- round(median(as.numeric(df$interview_duration), na.rm = T),0)

survey_lenght$Overall_median <-  overall_survey_median

# Enumerator with short interv duration
short_interviews_by_enum <- df %>% 
  filter(df$consent == "yes" & population_group != "not_eligible") %>% 
  dplyr::filter(interview_duration < time_limit & today > "2020-07-20") %>% 
  
  dplyr::select(Date = today, 
                Enumerator = enumerator_num, 
                Governorate = governorate_mcna_r, 
                Location = district_mcna,
                Duration =  interview_duration
  ) %>% mutate(
    Interview_Type = case_when(is.na(Governorate) ~ "in person",
                               TRUE ~ "remote"),
    Duration = round(Duration,0),
  ) %>% 
  arrange(desc(Date) )

################################################################################################
### leaflet maps
# import governorate geojson
irq_gov <- st_read("input/spatial_data/irq_gov.geojson") 

irq_gov <- sf::st_as_sf(irq_gov, coords = c("long", "lat"), crs = 4326)
irq_gov <- sf::st_cast(irq_gov,"POLYGON") 

# gov labels
gov_labels <- st_read("input/spatial_data/gov_labels.geojson")

gov_labels_halo <- sprintf(
  '<strong><span style="font-size: 10px; color: #FFFFFF">%s</span></strong>',
  gov_labels$ADM1_EN) %>% 
  lapply(htmltools::HTML)

# interview point tooltip
interview_tooltip <- sprintf(
  '<strong><span style="font-size: 10px; color: #EE5859;font-family:Arial;">%s</span><br><span style="font-size: 8px; color: #58585A;"> %s Governorate</strong></span><br><span style="font-size: 8px; color: #58585A;"><strong>Cluster ID: %s</strong></span>',
  district_join$district_gps, district_join$governorate_mcna, district_join$cluster_location_id)%>% 
  lapply(htmltools::HTML)

# district tooltip
district_tooltip <- sprintf(
  '<strong><span style="font-size: 8px; color: #58585A;font-family:Arial;">%s District</span><br><span style="font-size: 7px; color: #58585A;"> %s Governorate</strong></span>',
  irq_dist$ADM2_EN, irq_dist$ADM1_EN)%>% 
  lapply(htmltools::HTML)

# IDP remote interviews district tooltip
idp_district_tooltip <- sprintf(
  '<strong><span style="font-size: 12px; color: #58585A;font-family:Arial;">%s </span><br><span style="font-size: 10px; color: #58585A;"> %s </strong></span><br>
  <span style="font-size: 10px; color: #58585A;font-family:Arial;">%s percent complete</span><br>
  <span style="font-size: 8px; color: #58585A;font-family:Arial;">%s Interviews Completed</span><br>
  <span style="font-size: 8px; color: #58585A;font-family:Arial;">%s Interviews Remaining </span>',
  iraq_dist_idp$ADM2_EN, iraq_dist_idp$ADM1_EN, iraq_dist_idp$final_perc_complete, iraq_dist_idp$final_accepted, iraq_dist_idp$final_remaining)%>% 
  lapply(htmltools::HTML)

# returnees remote interviews district tooltip
returnee_district_tooltip <- sprintf(
  '<strong><span style="font-size: 12px; color: #58585A;font-family:Arial;">%s </span><br><span style="font-size: 10px; color: #58585A;"> %s </strong></span><br>
  <span style="font-size: 10px; color: #58585A;font-family:Arial;">%s percent complete</span><br>
  <span style="font-size: 8px; color: #58585A;font-family:Arial;">%s Interviews Completed </span><br>
  <span style="font-size: 8px; color: #58585A;font-family:Arial;">%s Interviews Remaining </span>',
  iraq_dist_returnee$ADM2_EN, iraq_dist_returnee$ADM1_EN, iraq_dist_returnee$final_perc_complete, iraq_dist_returnee$final_accepted, iraq_dist_returnee$final_remaining)%>% 
  lapply(htmltools::HTML)

# color palettes
idp_pal <- colorNumeric(
  palette = colorRampPalette(c('#F06E6F','#ffffbf', '#72966E'))(length(iraq_dist_idp$final_perc_complete)), 
  domain = iraq_dist_idp$final_perc_complete)

returnee_pal <- colorNumeric(
  palette = colorRampPalette(c('#F06E6F', '#ffffbf', '#72966E'))(length(iraq_dist_returnee$final_perc_complete)),
  domain = iraq_dist_returnee$final_perc_complete)

## leaflet
leaflet_map <-  leaflet(option=leafletOptions(zoomControl=FALSE,doubleClickZoom= TRUE,zoomSnap = 0.01),width = "100%", height = "600px") %>%
    addPolygons(
              data = irq_dist,
              color = "#58585A",
              fillColor =  "#E3E6E6",
              weight = 0.1,
              smoothFactor = 0.5,
              opacity = 1.0,
              fillOpacity = 0.8,
              label = district_tooltip,
              group="IDP",
              highlightOptions = highlightOptions(fillColor="white",
                                                 fillOpacity = 0.5,
                    color="white",
                    weight = 1.4,
                    bringToFront = F),
              ) %>%
    addPolygons(
              data = irq_dist,
              color = "#58585A",
              fillColor =  "#E3E6E6",
              weight = 0.1,
              smoothFactor = 0.5,
              opacity = 1.0,
              fillOpacity = 0.8,
              label = district_tooltip,
              group="Returnee",
              highlightOptions = highlightOptions(fillColor="white",
                                                 fillOpacity = 0.5,
                    color="white",
                    weight = 1.4,
                    bringToFront = F),
              ) %>%
  addPolygons(
              data = iraq_dist_idp,
              color = "#58585A",
              fillColor =  ~ idp_pal(final_perc_complete),
              weight = 0.2,
              smoothFactor = 0.5,
              opacity = 1.0,
              fillOpacity = 0.8,
              label = idp_district_tooltip,
              group="IDP",
              highlightOptions = highlightOptions(fillColor="white",
                                                 fillOpacity = 0.5,
                    color="white",
                    weight = 1.4,
                    bringToFront = F),
              ) %>%
    addPolygons(
              data = iraq_dist_returnee,
              color = "#58585A",
              fillColor =  ~ returnee_pal(final_perc_complete),
              weight = 0.2,
              smoothFactor = 0.5,
              opacity = 1.0,
              fillOpacity = 0.8,
              label = returnee_district_tooltip,
              group="Returnee",
              highlightOptions = highlightOptions(fillColor="white",
                                                 fillOpacity = 0.5,
                    color="white",
                    weight = 1.4,
                    bringToFront = F),
              ) %>%
  addPolylines(data=irq_gov,
             color = "#58585A",
             weight = 1.1,
             opacity = 1.0,
             group="IDP",
             options = list(zIndex = 300)) %>% 
    addPolylines(data=irq_gov,
             color = "#58585A",
             weight = 1.1,
             opacity = 1.0,
             group="Returnee",
             options = list(zIndex = 300)) %>% 
          # addLabelOnlyMarkers(data= gov_labels,
          #                   label = gov_labels_halo,
          #                   group = "IDP",
          #                   labelOptions = labelOptions(noHide = T,
          #                                               direction = 'center',
          #                                               textOnly = T,
          #                                               style = list(
          #                                                 "padding" = "3px 8px",
          #                                                 "font-family" = "Arial",
          #                                                 "text-shadow"="2px 2px 5px #58585A"
          #                                               ))) %>%
      
          addLayersControl(
            baseGroups = c("IDP","Returnee"),
            options = layersControlOptions(collapsed = F)
          )


```

<center> **Data Collection Monitoring Report** </center>


# {.tabset}

## Interactive Map

```{r eval=TRUE, echo=FALSE, results='asis'}
leaflet_map
```

***
## Progress Statistics

<center>**Number surveys per day of data collection** </center> </br>

```{r eval=TRUE, echo=FALSE, results='asis'}
kable(survey_status_per_day)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
```
  


<center>**Interview Method - Completed Interviews**</center> </br>

```{r eval=TRUE, echo=FALSE, results='asis'}

kable(interview_method_wide)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
```

***

## Enumerator Productivity

<center>**Number of surveys per day by enumerator** </center> </br>

```{r eval=TRUE, echo=FALSE, results='asis'}

DT::datatable(enumer_per_survey_status,
              options = list(
                  pageLength = 2000,
                  dom = 'ft'
                )
  ) %>% 
  DT::formatStyle('Deleted',  color = 'red', fontWeight = 'bold') %>% 
  DT::formatStyle('Accepted',  color = 'green', fontWeight = 'bold')

```


## General Checks  

<center>**surveys collected in under `r time_limit` minutes - last 7 days** </center> </br>
  
```{r eval=TRUE, echo=FALSE, results='asis'}
kable(short_interviews_by_enum)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
```

***

<center>**Surveyors with very low or high productivity** </center> </br>

```{r eval=TRUE, echo=FALSE, results='asis'}
kable(enumerator_productivity_final)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
```

***



<center>**Median interview duration by enumerator** </center> </br>

```{r eval=TRUE, echo=FALSE, results='asis'}
kable(survey_lenght)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
```
<center>**Surveys made before the first day of data collection (**`r assessment_start_date`**)**</center> </br>

```{r eval=TRUE, echo=FALSE, results='asis'}
kable(started_before)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
```


***


## Phone Interviews Tracking

```{r eval=TRUE, echo=FALSE, results='asis'}
DT::datatable(district_tracking_merged_phone,
              options = list(
                  pageLength = 130,
                  dom = 'ft'
                )
              ) %>% 
  DT::formatStyle('Deleted',  color = 'red', fontWeight = 'bold') %>% 
  DT::formatStyle('Accepted',  color = 'green', fontWeight = 'bold') %>% 
  DT::formatStyle('Short_intv',  color = 'red', fontWeight = 'bold') %>%
  DT::formatStyle('Remaining', fontWeight = 'bold')%>% 
  DT::formatStyle('Remaining_Max', fontWeight = 'bold')
```

## In person Interviews Tracking

```{r eval=TRUE, echo=FALSE, results='asis'}
DT::datatable(district_tracking_merged_in_person,
              options = list(
                  pageLength = 130,
                  dom = 'ft')
              ) %>% 
  DT::formatStyle('Deleted',  color = 'red', fontWeight = 'bold') %>% 
  DT::formatStyle('Accepted',  color = 'green', fontWeight = 'bold') %>% 
  DT::formatStyle('Short_intv',  color = 'red', fontWeight = 'bold') %>%
  DT::formatStyle('Remaining', fontWeight = 'bold') 
```

